Imminent range shifts in transboundary fish stocks challenge their management under climate change

### 2021-05-21 Scripts/Manuscript.Rmd
I cluded William's comments

**Most management plans that are not designed or prepared to respond to range and abundance shifts will be less resilient to climate change [@Miller:2013iv; @Sumaila:2020tp]. Focusing on identified “hotspots” is key to anticipating a potential increase in and averting fisheries conflicts in coming years. Identified strategies to cope with changes in the shared proportion of transboundary stocks include strengthening of current cooperative mechanisms and the consideration of side payments, which do not have to be monetary [@Tunca:2019if; @Miller:2013iv], increased international cooperation [@Miller:2013iv] and management rules that capture distributional shifts [@PalaciosAbrantes:2020vt; @Pinsky:2018cb]. Some examples of current treaties that have adapted some of these strategies include: the Pacific Salmon Treaty between Canada and the U.S. to manage Pacific salmon (Oncorhynchus sp.) and which has a conservation fund functioning as a side payment [@Miller:2013iv], the International Pacific Halibut Commission between Canada and the United States, which as the name implies manages Pacific halibut (*Hippoglossus stenolepis*) and allocates quota based on the stock’s yearly distribution [@PalaciosAbrantes:2020vt]; and the Parties to the Nauru Agreement (PNA) an Oceania subregional agreement among 8 Pacific Island countries and Tokelau, which collectively manage the largest tuna fishery in the world, controlling around 50% of the global supply of skipjack tuna (*Katsuwonus pelamis*). The PNA manage fishing effort under a so-called Vessel Day Scheme, an adaptive and equitable system which accounts for shifts in stocks and catches as a result of climate variability [@Aqorau:2018bh]. Quota allocation methods based on a stock’s current distribution and/or according to fixed-historical proportions like that of the European Union need to evolve to be more agile [@Baudron:2020dj] and potentially move towards a dynamic method or a combination of both [@PalaciosAbrantes:2020vt; @Sumaila:2020tp].**

>>>>

**Most management plans that are not designed or prepared to respond to range and abundance shifts will be less resilient to climate change [@Miller:2013iv; @Sumaila:2020tp]. Focusing on identified “hotspots” will help anticipate any potential increases in and averting fisheries conflicts in coming years. Identified strategies to cope with changes in the shared proportion of transboundary stocks include strengthening of current cooperative mechanisms and the consideration of side payments (including non-monetary arrangements) [@Tunca:2019if; @Miller:2013iv], increased international cooperation [@Miller:2013iv] and management rules that capture distributional shifts [@PalaciosAbrantes:2020vt; @Pinsky:2018cb]. Some examples of current treaties that have adapted some of these strategies include: the Pacific Salmon Treaty between Canada and the U.S. to manage Pacific salmon (Oncorhynchus sp.) and which has a conservation fund functioning as a side payment [@Miller:2013iv], the International Pacific Halibut Commission between Canada and the United States, which as the name implies manages Pacific halibut (*Hippoglossus stenolepis*) and allocates quota based on the stock’s yearly distribution [@PalaciosAbrantes:2020vt]; and the Parties to the Nauru Agreement (PNA) an Oceania subregional agreement among 8 Pacific Island countries and Tokelau, which collectively manage the largest tuna fishery in the world, controlling around 50% of the global supply of skipjack tuna (*Katsuwonus pelamis*). The PNA manage fishing effort under a so-called Vessel Day Scheme, an adaptive and equitable system which accounts for shifts in stocks and catches as a result of climate variability [@Aqorau:2018bh]. Quota allocation methods based on a stock’s current distribution and/or according to fixed-historical proportions like that of the European Union need to evolve to be more agile [@Baudron:2020dj] and potentially move towards a dynamic method or a combination of both [@PalaciosAbrantes:2020vt; @Sumaila:2020tp].**
